---
title: BACS-hw06-107070004
output:
  pdf_document:
mainfont: LiberationSerif
sansfont: LiberationSans
monofont: LiberationMono
---

# Question 1)

The Verizon dataset this week is provided as a “wide” data frame. Let’s practice reshaping it to a “long” data frame. You may use either shape (wide or long) for your analyses in later questions.

```{r}
verizon <- read.csv("verizon_wide.csv", header=TRUE)
```

## (a) Pick a reshaping package (we discussed two in class) – research them online and tell us why you picked it over others (provide any helpful links that supported your decision).

```{r, include=FALSE}
# ILEC <- na.omit(verizon$ILEC)
# CLEC <- na.omit(verizon$CLEC)

# loads_long <- data.frame(
#   load_time= c(ILEC, CLEC),
#   host = c(rep("ILEC", length(ILEC)),
#   rep("CLEC", length(CLEC)))
# )
```

- https://jtr13.github.io/spring19/hx2259_qz2351.html

  - The gather() function only uses the first column to create the key-value pair, therefore we should comsider more.
  - melt() function treat “variable(host)” as an “id variable” and always produces a correct long form dataset.

## (b) Show the code to reshape the versizon_wide.csv data

```{r}
install.packages("reshape",repos = "http://cran.us.r-project.org")
library(reshape)
loads_long <- melt(verizon, na.rm = TRUE,
                    variable.names = "host",
                    value.names = "load_time")
```

## (c) Show us the “head” and “tail” of the data to show that the reshaping worked

```{r}
head(loads_long)
tail(loads_long)
```

## (d) Visualize Verizon’s response times for ILEC vs. CLEC customers

```{r}
hosts <- split(x=loads_long$value, f=loads_long$variable)
plot(density(hosts$ILEC), col="cornflowerblue", lwd=2, xlim=c(0, 200))
lines(density(hosts$CLEC), col="coral3", lwd=2)
legend(300, 0.5, lty=1, c("ILEC", "CLEC"), col=c("cornflowerblue", "coral3"))
```

# Question 2)

Let’s test if the mean of response times for CLEC customers is greater than for ILEC customers.

## (a) State the appropriate null and alternative hypotheses (one-tailed)

H0 : ILEC = CLEC
H1 : ILEC < CLEC

## (b) Use the appropriate form of the t.test() function to test the difference between the mean of ILEC versus CLEC response times at 1% significance. For each of the following tests, show us the results and tell us whether you would reject the null hypothesis.

### (i) Conduct the test assuming variances of the two populations are equal

```{r}
t.test(hosts$ILEC, hosts$CLEC, conf.level = 0.99, alternative = "two.sided", var.equal=TRUE)
```

Since p-value(0.09068) < significant level(0.01), reject H0.

### (ii) Conduct the test assuming variances of the two populations are not equal

```{r}
t.test(hosts$ILEC, hosts$CLEC, conf.level = 0.99, alternative = "two.sided", var.equal=FALSE)
```

Since p-value(0.05975) > significant level(0.01), don‘t reject H0.

## (c) Use a permutation test to compare the means of ILEC vs. CLEC response times

```{r}
permute_diff <- function(values, groups) {
  permuted <- sample(values, replace = FALSE)
  grouped <- split(permuted, groups)
  permuted_diff <- mean(grouped$ILEC) - mean(grouped$CLEC)
}
nperms <- 10000
permuted_diffs <- replicate(nperms, permute_diff(loads_long$value,loads_long$variable))
```

### (i) Visualize the distribution of permuted differences, and indicate the observed difference as well.

```{r}
observed_diff <- mean(hosts$ILEC) - mean(hosts$CLEC)
observed_diff
hist(permuted_diffs, breaks = "fd", probability = TRUE)
lines(density(permuted_diffs),lwd=2)
abline(v=observed_diff, col="cornflowerblue", lwd = 2)
```

### (ii) What are the one-tailed and two-tailed p-values of the permutation test?

```{r}
p_1tailed <- sum(permuted_diffs>observed_diff) /nperms
p_1tailed
p_2tailed <- sum(abs(permuted_diffs)>observed_diff) /nperms
p_2tailed
```

### (iii) Would you reject the null hypothesis at 1% significance in a one-tailed test?

The p value > (1-99%)/2, the claim is included in the 99% null distribution.

# Question 3)

Let’s use the Wilcoxon test to see if the response times for CLEC are different than ILEC.

## (a) Compute the W statistic comparing the values. You may use either the permutation approach (with either for-loops or the vectorized form) or the rank sum approach.

```{r}
gt_eq <- function(a, b) {ifelse(a > b, 1, 0) +ifelse(a == b, 0.5, 0)}
W <- sum(outer(hosts$CLEC, hosts$ILEC, FUN =gt_eq))
W 
```

## (b) Compute the one-tailed p-value for W.

```{r}
n1 <- length(hosts$CLEC)
n2 <- length(hosts$ILEC)
wilcox_p_1tail <- 1 - pwilcox(W, n1, n2)
wilcox_p_1tail
wilcox_p_2tail <- 2 * wilcox_p_1tail
wilcox_p_2tail
```

## (c) Run the Wilcoxon Test again using the wilcox.test() function in R – make sure you get the same W as part [a]. Show the results.

```{r}
wilcox.test(hosts$CLEC, hosts$ILEC, alternative = "two.sided")
```

## (d) At 1% significance, and one-tailed, would you reject the null hypothesis that the values of CLEC and ILEC are different from one another?

```{r}
wilcox.test(hosts$CLEC, hosts$ILEC, conf.level = 0.99, alternative = "greater")
```

The p value(0.0004565) < (1-99%)/2, reject H0.

# Question 4)

One of the assumptions of some classical statistical tests is that our population data should be roughly normal. Let’s explore one way of visualizing whether a sample of data is normally distributed.

## (a) Follow the following steps to create a function to see how a distribution of values compares to a perfectly normal distribution. The ellipses (...) in the steps below indicate where you should write your own code.

### Make a function called norm_qq_plot() that takes a set of values):

```{r}
norm_qq_plot <- function(values) {
  probs1000 <- seq(0, 1, 0.001)
  q_vals <- quantile(values, probs=probs1000)
  q_norm <- qnorm(probs1000, mean=mean(values), sd=sd(values))
  plot(q_norm, q_vals, xlab="normal quantiles", ylab="values quantiles")
  abline(a=0, b=1, col="red", lwd=2)
}
```

## (b) Confirm that your function works by running it against the values of our d123 distribution from week 3 and checking that it looks like the plot on the right:

```{r}
set.seed(978234)
d1 <- rnorm(n=500, mean=15, sd=5)
d2 <- rnorm(n=200, mean=30, sd=5)
d3 <- rnorm(n=100, mean=45, sd=5)
d123 <- c(d1, d2, d3)

plot(density(d123))
norm_qq_plot(d123)
```

## (c) Use your normal Q-Q plot function to check if the values from each of the CLEC and ILEC samples we compared in question 2 could be normally distributed. What’s your conclusion?

```{r}
norm_qq_plot(hosts$ILEC)
norm_qq_plot(hosts$CLEC)
```

- ILEC's plot is "Skwed Right" histogram, due to the upper tail is a little bit far away from red line.
- CLEC's plot is normally distributed, because of its symmetry.
