---
title: BACS-hw01-107070004
output:
    pdf_document:
#         latex_engine: xelatex
# mainfont: LiberationSerif
# sansfont: LiberationSans
# monofont: LiberationMono
---

1. What is the 5th element in the original list of ages?


```{r knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 50), tidy = TRUE)}
customers <- read.table('/Users/jessica/Desktop/BACS/hw1/customers.txt', header = TRUE)
ages <- customers$age
ages[5]
```

2. What is the fifth lowest age?

```{r}
sorted_ages <- sort(ages)
sorted_ages[5]
```

3. Extract the five lowest ages together
HINT: to get a sequence of numbers from a list, you can use:
	my_list[c(1,2,3,4,5)]   but can you think of a shorter or clearer way of doing this?

```{r}
sorted_ages[1:5]
```

4. Get the five highest ages by first sorting them in decreasing order first.
HINT: find out how to sort in decreasing order by using:  help(sort) or  ?sort

```{r}
sort(ages, decreasing = TRUE)[1:5]
```

5. What is the average (mean) age?

```{r}
mean(ages)
```

6. What is the standard deviation of ages? (guess or google the standard deviation function in R)

```{r}
sd(ages)
```

7. Make a new variable called age_diff, with the difference between each age and the mean age

```{r}
age_diff = ages - mean(ages)
age_diff
```

8. What is the average “difference between each age and the mean age”?
HINT: think carefully why someone would want to know this, and what it implies about how to do #7

```{r}
mean(age_diff)
```

9. Visualize the raw data as we did in class: (a) histogram, (b) density plot, (c) boxplot+stripchart


```{r, echo=FALSE, fig.width=6, fig.asp=0.618, out.width="50%", fig.align="default"}
hist(ages, main="(a) histogram")
plot(density(ages), main="(b) density plot")
boxplot(ages, horizontal=TRUE, main="(c) boxplot+stripchart")
stripchart(ages, method="stack", add=TRUE)
```