---
title: BACS-hw12-107070004
output:
  pdf_document:
mainfont: LiberationSerif
sansfont: LiberationSans
monofont: LiberationMono
---

Let’s take another look at interactions in our cars dataset. For this week, let’s only use the following data:

1. mpg: miles-per-gallon (dependent variable)
2. weight: weight of car
3. acceleration: acceleration ability of car (seconds to achieve 0-60mph)
4. model_year: year model was released
5. origin: place car was designed (1: USA, 2: Europe, 3: Japan)
6. cylinders: cylinders in engine (only used in Question 3)

Create a data.frame called cars_log with log-transformed columns for mpg, weight, and acceleration
(model_year and origin don’t have to be transformed)

# Question 1) Let’s visualize how weight and acceleration are related to mpg.

```{r}
cars <- read.table("auto-data.txt", header=FALSE, na.strings = "?")
names(cars) <- c("mpg", "cylinders", "displacement", "horsepower", "weight",
                 "acceleration", "model_year", "origin", "car_name")
cars_log <- with(cars, data.frame(log(mpg), log(weight), log(acceleration)
                                  , log(cylinders), model_year, origin))
head(cars_log, 10)
```

## (a) Let’s visualize how weight might moderate the relationship between acceleration and mpg:

### (i) Create two subsets of your data, one for light-weight cars (less than mean weight) and one for heavy cars (higher than the mean weight)

```{r}
cars_log_sorted <- cars_log[order(cars_log$log.weight.),]
head(cars_log_sorted, 5)
len <- nrow(cars_log_sorted)
len
heavy_cars <- cars_log_sorted[c(0:len/2),]
tail(heavy_cars, 5)
light_cars <- cars_log_sorted[c(len/2+1:len),]
head(light_cars, 5)
```

_HINT: consider carefully how you compare log weights to mean weight_

### (ii) Create a single scatter plot of acceleration vs. mpg, with different colors and/or shapes for light versus heavy cars

plot is show in (iii)

### (iii) Draw two slopes of acceleration-vs-mpg over the scatter plot: one slope for light cars and one slope for heavy cars (distinguish them by appearance)

```{r}
plot(heavy_cars$log.acceleration., heavy_cars$log.mpg.
    , main="single scatter plot of acceleration vs. mpg"
    , xlab = "log.acceleration.", ylab = "log.mpg."
    , xlim=c(2, 3.5), ylim=c(2, 4.5)
    , col = "red", pch = 19)
points(light_cars$log.acceleration., light_cars$log.mpg.
    , col = "green", pch = 19)
legend("topleft", legend = c("light cars", "heavy cars"),
       lwd = 3, lty = c(1, 1), col = c("red", "green"))

regr_heavy_a <- lm(log.mpg. ~ log.acceleration.
              , data=heavy_cars, na.action=na.exclude)
regr_light_a <- lm(log.mpg. ~ log.acceleration.
              , data=light_cars, na.action=na.exclude)
abline(regr_heavy_a, col = "red", lwd = 3)
abline(regr_light_a, col = "green", lwd = 3)
```

## (b) Report the full summaries of two separate regressions for light and heavy cars where log.mpg. is dependent on log.weight., log.acceleration., model_year and origin

```{r}
regr_heavy_b <- lm(log.mpg. ~ log.weight. + log.acceleration.
                  + model_year + factor(origin)
                  , data=heavy_cars, na.action=na.exclude)
regr_light_b <- lm(log.mpg. ~ log.weight. + log.acceleration.
                  + model_year + factor(origin)
                  , data=light_cars, na.action=na.exclude)
summary(regr_heavy_b)
summary(regr_light_b)
```

## (c) (not graded) 

# Question 2) Let’s tackle multicollinearity next. Consider the regression model:

## (a) (not graded) 

## (b) Use various regression models to model the possible moderation on log.mpg.: (use log.weight., log.acceleration., model_year and origin as independent variables)

### (i) Report a regression without any interaction terms

```{r}
regr_o <- lm(log.mpg. ~ log.weight. + log.acceleration.
                  + model_year + factor(origin)
              , data=cars_log, na.action=na.exclude)
summary(regr_o)
```

### (ii) Report a regression with an interaction between weight and acceleration

```{r}
regr_wa <- lm(log.mpg. ~ log.weight. + log.acceleration.
                  + model_year + factor(origin)
                  + log.weight.*log.acceleration.
              , data=cars_log, na.action=na.exclude)
summary(regr_wa)
```

### (iii) Report a regression with a mean-centered interaction term

```{r}
cars_log_mc <-  data.frame(scale(cars_log,center=TRUE,scale=FALSE))
regr_mc <- lm(log.mpg. ~ cars_log_mc$log.weight. + cars_log_mc$log.acceleration.
                  + cars_log_mc$model_year + factor(cars_log_mc$origin)
                  + cars_log_mc$log.weight.*cars_log_mc$log.acceleration.
              , data=cars_log)
summary(regr_mc)
```

### (iv) Report a regression with an orthogonalized interaction term

```{r}
interaction_regr <- lm(log.weight.*log.acceleration. ~ log.weight. + log.acceleration.
                      + model_year + factor(origin)
                      , data=cars_log)
interaction_ortho <- interaction_regr$residuals
regr_ortho <- lm(log.mpg. ~ log.weight. + log.acceleration.
                  + model_year + factor(origin)
                  + interaction_ortho
              , data=cars_log)
summary(regr_ortho)
```

## (c) For each of the interaction term strategies above (raw, mean-centered, orthogonalized) what is the correlation between that interaction term and the two variables that you multiplied together?

* raw

```{r}
cor(cars_log$log.weight., cars_log$log.weight.*cars_log$log.acceleration.)
cor(cars_log$log.acceleration., cars_log$log.weight.*cars_log$log.acceleration.)

```

* mean-centered

```{r}
cor(cars_log_mc$log.weight., cars_log_mc$log.weight.*cars_log_mc$log.acceleration.)
cor(cars_log_mc$log.acceleration., cars_log_mc$log.weight.*cars_log_mc$log.acceleration.)
```

* orthogonalized

```{r}
cor(cars_log$log.weight., interaction_ortho)
cor(cars_log$log.acceleration., interaction_ortho)
```

# Question 3) We saw earlier that the number of cylinders does not seem to directly influence mpg when car weight is also considered. But might cylinders have an indirect relationship with mpg through its weight?

Let’s check whether weight mediates the relationship between cylinders and mpg, even when other factors are controlled for. Use log.mpg., log.weight., and log.cylinders as your main variables, and keep log.acceleration., model_year, and origin as control variables (see gray variables in diagram).

## (a) Let’s try computing the direct effects first:

### (i) Model 1: Regress log.weight. over log.cylinders. only (check whether number of cylinders has a significant direct effect on weight)

```{r}
regr_wc <- lm(log.weight. ~ log.cylinders., data=cars_log)
summary(regr_wc)
```
ans: Number of cylinders has a significant direct effect on weight.

### (ii) Model 2: Regress log.mpg. over log.weight. and all control variables (check whether weight has a significant direct effect on mpg with other variables statistically controlled?)

```{r}
regr_mw <- lm(log.mpg. ~  log.weight. + log.acceleration. + log.cylinders.
                  + model_year + factor(origin)
                  , data=cars_log)
summary(regr_mw)
```
ans: Weight has a significant direct effect on mpg with other variables statistically controlled.

## (b) What is the indirect effect of cylinders on mpg? (use the product of slopes between model 1 & 2)

```{r}
regr_wc$coefficients[2]*regr_mw$coefficients[2]
```

## (c) Let’s bootstrap for the confidence interval of the indirect effect of cylinders on mpg

### (i) Bootstrap regression models 1 & 2, and compute the indirect effect each time: what is its 95% CI of the indirect effect of log.cylinders. on log.mpg.?

```{r}
boot_mediation <- function(model1, model2, dataset) {
  boot_index <- sample(1:nrow(dataset), replace=TRUE)
  data_boot <- dataset[boot_index, ]
  regr1 <- lm(model1, data_boot)
  regr2 <- lm(model2, data_boot)
  return(regr1$coefficients[2] *regr2$coefficients[2])
}
set.seed(42)
indirect <- replicate(2000, boot_mediation(regr_wc,regr_mw, cars_log))
quantile(indirect, probs=c(0.025, 0.975))
```

### (ii) Show a density plot of the distribution of the 95% CI of the indirect effect

```{r}
plot(density(indirect), main="the distribution of the 95% CI of the indirect effect")
abline(v=quantile(indirect, probs=c(0.025, 0.975)))
```