---
title: BACS-hw03-107070004
output: pdf_document
mainfont: LiberationSerif
sansfont: LiberationSans
monofont: LiberationMono
---

```{r, include=FALSE}
bookings <- read.table("first_bookings_datetime_sample.txt", header=TRUE)
bookings$datetime[1:9]
hours  <- as.POSIXlt(bookings$datetime, format="%m/%d/%Y %H:%M")$hour
mins   <- as.POSIXlt(bookings$datetime, format="%m/%d/%Y %H:%M")$min
minday <- hours*60 + mins
# plot(density(minday), main="Minute (of the day) of first ever booking", col="blue", lwd=2)
```

# Question 3)

The startup company EZTABLE has an online restaurant reservation system that is accessible by mobile and web.
Imagine that EZTABLE would like to start a promotion for new members to make their bookings earlier in the day.

## a) What is the “average” booking time for new members making their first restaurant booking?(use minday, which is the absolute minute of the day from 0-1440)

```{r}
mean(minday)
```

### i) Use traditional statistical methods to estimate the population mean of minday, its standard error, and the 95% confidence interval (CI) of the sampling means

```{r}
visualize_95_mean_ci <- function(sample) {
  sample_means <- mean(sample)
  sample_size <- length(sample)
  sample_stdevs <- sd(sample)
  sample_stderrs <- sample_stdevs/sqrt(sample_size)
  ci95_low  <- sample_means - sample_stderrs*1.96
  ci95_high <- sample_means + sample_stderrs*1.96
  cat("The 95% confidence interval (CI) is", mean(abs(ci95_high -ci95_low)));
}
```

```{r}
mean(minday)
std_error <- sd(minday)/sqrt(length(minday))
std_error
visualize_95_mean_ci(minday)
```

### ii) Bootstrap to produce 2000 new samples from the original sample

```{r}
sample_size <- 2000
sample0 <- sample(minday, sample_size)
minday.resemples <- replicate(2000, sample(minday, length(minday), replace=TRUE))
```

### iii) Visualize the means of the 2000 bootstrapped samples

```{r}
  plot(density(minday.resemples), lwd=2, main="means of bootstrapped samples")
  plot_resample_mean<-function(sample_i) {
    abline(v=mean(sample_i), col=rgb(0.0, 0.4, 0.0, 0.01))
  }
  apply(minday.resemples , 2, FUN = plot_resample_mean)
```

### iv) Estimate the 95% CI of the bootstrapped means.

```{r}
  sample_means <- apply(minday.resemples, 2, FUN=mean)
  quantile(sample_means, probs = c(0.025, 0.975))
```

## b) By what time of day, have half the new members of the day already arrived at their restaurant?

```{r}
  hour <- round(median(minday)/60, 0)
  minute <- median(minday)%%60
  cat(hour,":",minute)
```

### i) Estimate the median of minday

```{r}
median(minday)
```

### ii) Visualize the medians of the 2000 bootstrapped samples

```{r}
  plot(density(minday.resemples), lwd=2, main="medians of bootstrapped samples")
  plot_resample_median<-function(sample_i) {
    abline(v=median(sample_i), col=rgb(0.0, 0.4, 0.0, 0.01))
  }
  apply(minday.resemples , 2, FUN = plot_resample_median)
```

### iii) Estimate the 95% CI of the bootstrapped medians.

```{r}
  sample_medians <- apply(minday.resemples, 2, FUN=median)
  quantile(sample_medians, probs = c(0.025, 0.975))
```