---
title: BACS-hw15-107070004
output:
  pdf_document:
mainfont: LiberationSerif
sansfont: LiberationSans
monofont: LiberationMono
always_allow_html: true
---

```{r, include=FALSE}
install.packages("seminr",repos = "http://cran.us.r-project.org")
library(seminr)
install.packages("semPlot",repos = "http://cran.us.r-project.org")
library(semPlot)
```

```{r}
sd <- read.csv("./security_data_sem.csv")
```

# Question 1) Composite Path Models using PLS-PM

## (a) Create a PLS path model using SEMinR, with all the following characteristics:

### (i) Measurement model – all constructs are measured as composites:

1. Trust in website (TRUST): items TRST1 - TRST4
2. Perceived security of website (SEC): items PSEC1 - PSEC4
3. Reputation of website (REP): items PREP1 - PREP4
4. Investment in website (INV): items PINV1 - PINV3
5. Perception of privacy policies (POL): items PPSS1 - PPSS3
6. Familiarity with website (FAML): item FAML1
   (see the documentation of SEMinR for making single item constructs)
7. Interaction between REP and POL (use orthogonalized product terms)

```{r}
# Measurement Models
sd_mm <- constructs(
  composite("TRUST",multi_items("TRST", 1:4)),
  composite("SEC",multi_items("PSEC", 1:4)),
  composite("REP",multi_items("PREP", 1:4)),
  composite("INV",multi_items("PINV", 1:3)),
  composite("POL",multi_items("PPSS", 1:3)),
  composite("FAML",multi_items("FAML", 1:1)),
  interaction_term(iv="REP", moderator="POL", method=orthogonal)
)
```

### (ii) Structural Model – paths between constructs as shown in this causal model:

REP + INV + POL + FAML + (REPxPOL) -> SEC -> TRUST

```{r}
#Structural Models
sd_sm <- relationships(
  paths(from= c("REP", "INV", "POL", "FAML", "REP*POL"),to= "SEC"),
  paths(from= "SEC",to= "TRUST")
)
```

## (b) Show us the following results in table or figure formats:

```{r}
sd_pls <- estimate_pls(
  data = sd,
  measurement_model = sd_mm,
  structural_model = sd_sm
)
sd_result <- summary(sd_pls)
sd_result
```

### (i) Plot a figure of the estimated model

```{r}
plot(sd_pls)
```

### (ii) Weights and loadings of composites

```{r}
sd_result$weights
sd_result$loadings
```
### (iii) Regression coefficients of paths between factors

```{r}
sd_result$paths
```

### (iv) Bootstrapped path coefficients: t-values, 95% CI

```{r}
boot_sd <- bootstrap_model(sd_pls,nboot= 1000)
summary(boot_sd)
```

# Question 2) Common-Factor Models using CB-SEM

## (a) Create a common factor model using SEMinR, with the following characteristics:

### (i) Either respecify all the constructs as being reflective(), or use the as.reflective() function to convert your earlier measurement model to being entirely reflective.

```{r}
sd_cf_mm <- as.reflective(sd_mm)
```

### (ii) Use the same structural model as before (you can just reuse it again)

```{r}
sd_cf_pls <- estimate_cbsem(
  data = sd,
  measurement_model = sd_cf_mm,
  structural_model = sd_sm
)
sd_cf_report <- summary(sd_cf_pls)
sd_cf_report
```

## (b) Show us the following results in table or figure formats

### (i) Plot a figure of the estimated model (it will look different from your PLS model)

```{r}
plot(sd_cf_pls)
```

### (ii) Loadings of composites

```{r}
sd_cf_report$loadings
```

### (iii) Regression coefficients of paths between factors, and their p-values

```{r}
sd_cf_report$paths$coefficients
sd_cf_report$paths$pvalues
```

