---
title: BACS-hw07-107070004
output:
  pdf_document:
mainfont: LiberationSerif
sansfont: LiberationSans
monofont: LiberationMono
---

# Question 1)

Let’s develop some intuition about the data and results:

```{r, include=FALSE}
install.packages("plyr",repos = "http://cran.us.r-project.org")
install.packages("readr",repos = "http://cran.us.r-project.org")
library(plyr)
library(readr)
```

https://datascienceplus.com/how-to-import-multiple-csv-files-simultaneously-in-r-and-create-a-data-frame/

```{r, results='hide', warning=FALSE}
mydir = "pls-media"
myfiles = list.files(path=mydir, pattern="*.csv", full.names=TRUE)
dat_csv = ldply(myfiles, read_csv)
```

## (a) What are the means of viewers’ intentions to share (INTEND.0) on each of the four media types?

```{r}
by_media <- split(dat_csv , dat_csv$media)
by_media[1]
ans <- sapply(by_media[1], mean)
ans
```

## (b) Visualize the distribution and mean of intention to share, across all four media. (Your choice of data visualization; Try to put them all on the same plot and make it look sensible)

```{r}

```

## (c) From the visualization alone, do you feel that media type makes a difference on intention to share?

```{r}

```

# Question 2)

Let’s try traditional one-way ANOVA:

## (a) State the null and alternative hypotheses when comparing INTEND.0 across four groups in ANOVA

## (b) Let’s compute the F-statistic ourselves:

### (i) Show the code and results of computing MSTR, MSE, and F

```{r}

```

### (ii) Compute the p-value of F, from the null F-distribution; is the F-value significant? If so, state your conclusion for the hypotheses.

```{r}

```

## (c) Conduct the same one-way ANOVA using the aov() function in R – confirm that you got similar results.

```{r}

```

## (d) Regardless of your conclusions, conduct a post-hoc Tukey test (feel free to use the TukeyHSD() function in R) to see if any pairs of media have significantly different means – what do you find?

```{r}

```

## (e) Do you feel the classic requirements of one-way ANOVA were met? (Feel free to use any combination of methods we saw in class or any analysis we haven’t covered)

```{r}

```

# Question 3)

One of the assumptions of some classical statistical tests is that our population data should be roughly normal. Let’s explore one way of visualizing whether a sample of data is normally distributed.

## (a) State the null and alternative hypotheses (in terms of distribution or difference of mean ranks)

```{r}

```

## (b) Let’s compute (an approximate) Kruskal Wallis H ourselves:

### (i) Show the code and results of computing H

```{r}

```

### (ii) Compute the p-value of H, from the null chi-square distribution; is the H value significant? If so, state your conclusion of the hypotheses.

```{r}

```

## (c) Conduct the same test using the kruskal.wallis() function in R – confirm that you got similar results.

```{r}

```

## (d) Regardless of your conclusions, conduct a post-hoc Dunn test (feel free to use the dunnTest() function from the FSA package) to see if any pairs of media are significantly different – what do you find?

```{r}

```
